HPC--101\\Onboarding

### 2016-02-05 hpc_101/paper.tex
removed the cd action in example slides
fixed typo in globus endpoint
forgot to have the "source ~/.bash_profile" in the in slide examples...

\begin{frame}
	\frametitle{Globus}\footnotesize
\begin{block}{How do I get Globus?}
To utilize Globus, follow the following steps:
\begin{itemize}\tiny
\item Register for a Globus Online account -- \url{https://www.globusonline.org/signup}
\item Sign in to Globus Online (using your Globus Online username and password) -- \url{https://www.globusonline.org/signin}
\item Select ‘Start Transfer’ under ‘File Transfer’, or from the drop down menu in the top bar
\item You can view the list of available endpoints by clicking the button on the ‘Endpoint’ drop down box
\begin{itemize}\tiny
 \item Each of the login nodes is also an endpoint: \textbf{\emph{hawaii\#UHHPC1}} \& \textbf{\emph{hawaii\#UHHPC1}}
\end{itemize}
\item Once you select an endpoint, a login window will pop up. You can access the UHHPC endpoints by simply using your UH username and password. Enter your UH accounts username in the ‘Username’ field and UH accounts password in the ‘Password’ field and click ‘Authenticate’. 
\item You will see a listing of the contents of your home directory on the UH HPC. Double click on a directory to view its contents
\item Select a file or directory and click on the highlighted ‘arrow button’ to initiate the transfer
\end{itemize}
\end{block}
~\\
These instructions can also be found on the {\ci} website:~\\
{\footnotesize \href{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}}
\end{frame}

@@

@@

@@

%\section{Frequently Asked Questions}
\begin{frame}
\frametitle{FAQ}
\begin{itemize}\footnotesize
\item Are files on the cluster backed up?
  \begin{itemize}\tiny
  \item \textbf{Answer:} \textbf{NO!}  User files on the cluster \textbf{\emph{are not backed up}}.  It is up to you as the user to validate and maintain your own backups.  The {\citeam} takes no responsibility for any data that is lost due to human or mechanical error.  
  \end{itemize}

>>>>

\begin{frame}
	\frametitle{Globus}\footnotesize
\begin{block}{How do I get Globus?}
To utilize Globus, follow the following steps:
\begin{itemize}\tiny
\item Register for a Globus Online account -- \url{https://www.globusonline.org/signup}
\item Sign in to Globus Online (using your Globus Online username and password) -- \url{https://www.globusonline.org/signin}
\item Select ‘Start Transfer’ under ‘File Transfer’, or from the drop down menu in the top bar
\item You can view the list of available endpoints by clicking the button on the ‘Endpoint’ drop down box
\begin{itemize}\tiny
 \item Each of the login nodes is also an endpoint: \textbf{\emph{hawaii\#UHHPC1}} \& \textbf{\emph{hawaii\#UHHPC2}}
\end{itemize}
\item Once you select an endpoint, a login window will pop up. You can access the UHHPC endpoints by simply using your UH username and password. Enter your UH accounts username in the ‘Username’ field and UH accounts password in the ‘Password’ field and click ‘Authenticate’. 
\item You will see a listing of the contents of your home directory on the UH HPC. Double click on a directory to view its contents
\item Select a file or directory and click on the highlighted ‘arrow button’ to initiate the transfer
\end{itemize}
\end{block}
~\\
These instructions can also be found on the {\ci} website:~\\
{\footnotesize \href{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}{http://www.hawaii.edu/its/ci/hpc-resources/hpc-tutorials/globus-quick-start-guide/}}
\end{frame}

@@

source \ctilde/.bash_profile \#if you want to use modules or need environment variables, source your bash profile

@@

source \ctilde/.bash_profile \#if you want to use modules or need environment variables, source your bash profile

\#\# All options and environment variables found on schedMD site: \href{http://slurm.schedmd.com/sbatch.html}{http://slurm.schedmd.com/sbatch.html}
export OMP\_NUM\_THREADS=\$\{SLURM\_CPUS\_PER\_TASK\}

@@

\section{Frequently Asked Questions}
\begin{frame}
\frametitle{FAQ}
\begin{itemize}\footnotesize
\item Are files on the cluster backed up?
  \begin{itemize}\tiny
  \item \textbf{Answer:} \textbf{NO!}  User files on the cluster \textbf{\emph{are not backed up}}.  It is up to you as the user to validate and maintain your own backups.  The {\citeam} takes no responsibility for any data that is lost due to human or mechanical error.  
  \end{itemize}
